---
output:
  pdf_document: default
  html_document: default
---
```{r}
library(car)
library(reshape2)
library(ggplot2)
library(MASS)
library(interactions)

source("clean_data.R")


df <- remove_cols(df, c("Color", "Model"))

# Remove columns with only one observation and affected rows
res <- convert_categorical(df, categorical)
design <- as.data.frame(res$dummy)

singles <- c()
bad_idx <- c()
for (col in colnames(design)) {
  if (sum(design[, col] != 0) <= 1) {
    singles <- c(singles, col)
    bad_idx <- c(bad_idx, which(design[, col] != 0))
  }
}
singles
bad_idx

df <- df[-bad_idx, ]
```

## Box Cox
```{r}
bc <- boxcox(Price ~., data = df)
bc$x[which.max(bc$y)]
```

For the sake of interpretability, we will use a log transformation, since $\lambda \approx 0$.

## Iteratively Remove Multicollinear Regressors
```{r}
x <- df
model <- lm(log(Price) ~., data = x)
removed <- c()

finished <- F
while(!finished) {
  temp <- car::vif(model)[, "GVIF^(1/(2*Df))"]
  worst <- names(which.max(temp))
  if (length(temp) > 0 && temp[worst] > sqrt(5)) {
    x <- remove_cols(x, c(worst))
    model <- lm(log(Price) ~., data = x)

    removed <- c(removed, worst)
  } else {
    finished <- T
  }
}

removed
```

```{r}
which(abs(rstudent(model)) > 4)
```
After inspecting these data points, we do not find a good reason to remove them (i.e., they are not clerical errors).

```{r}
vif(model, type = "predictor")
```
We get that GVIF^(1/(2*Df)) $< 2.236068 \approx \sqrt5$ for all regressors, and no interactions are indicated, so there is likely no multicollinearity.

```{r}
plot(model)
```

## Backwards Stepwise Search
We do a backwards search since our model already conforms to the linear assumptions and is performing well. We simply wish to reduce the model size now.
```{r}
reduced_model <- step(model, direction = "backward", data = x, trace = 0, k = log(nrow(x)))
old <- names(model$coefficients)
new <- names(reduced_model$coefficients)

old[!(old %in% new)]
```
Location, seller type, owner type, and seating capacity were removed by BIC.

## Inspect Model Coefficients
```{r}
summary(reduced_model)
anova(reduced_model)
```

## Final Model Verification
```{r}
plot(reduced_model)
```


## Normalized Coefficients
```{r}
# removed by BIC. remember multicollinear rows are already removed
normalized <- remove_cols(x, c("Location", "Seating.Capacity", "Seller.Type", "Owner")) 


for (col in colnames(normalized)) {
  if (col != "Price" && !(col %in% categorical)) {
    normalized[, col] <- (normalized[, col] - mean(normalized[, col])) / sd(normalized[, col])
  }
}

normalized_model <- lm(log(Price) ~ ., data = normalized)
summary(normalized_model)

sort(abs(normalized_model$coefficients), decreasing = T)
```

## Confidence Intervals
```{r}
confint(normalized_model, level = 0.95)
```
